### 2019-08-04 report/chapter05.Rnw
Rewrite Chapter 03, analysis procedure and add some to discussion

@@

\section{Interpretation}
In this study, a proportion of the meta-analyses that have been scrutinized have publication bias. Since regression and rank test have been applied one-sided, they have very likely larger effects in smaller studies that in larger studies. \\
There have been proposed a number of reasons for this tendencies in smaller studies (see \citet{Egger} for a thorough discussion). In clinical settings, it might be that the requirement for more study participants in large studies might systematically change the study population. However, this systematic differences could influence the results in two ways: If recruitement of participants with a disease is difficult, and thus, also participants with less severe types of the disease are included, it might be that the effect of treatment is larger in the smaller study. But one could also argue that the opposite could eventually be the case. \\
The main cause for funnel plot asymmetry with smaller studies having larger effects is publication bias. Publication bias enforces questionable research practices from researchers such as selective outcome reporting, $p$-hacking and data fabrication. Larger studies are less affected, and have also in general higher methodological quality \citep{Egger}, which leads to smaller effect sizes.\\
Presence of publication bias in meta-analyses can ultimately lead to patient harm, because decision makers in clinical practice use the meta-analyses to take decisions if they use a treatment. On the swiss Cochrane website, it is stated that Cochrane is the ``single most reliable source of evidence on the effects of health care''. However, publication bias does in general lead to too large confidence in the results of the meta-analyses. In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias. Besides harm to patient, this can cause a waste of ressources. \\
The comparison of the results with previous analyses of publication bias in the Cochrane Database of Systematic Reviews implies gives more confidence in the results of this study, because they are largely in line. \\

@@

After application of the criteria of \citet{Ioannidis2007}, there are left \Sexpr{round((740/6354)*100, 1)} \% of the reviews and \Sexpr{round((23243/70662)*100, 1)}\% of the studies. It is not clear how the results would be in the remaining dataset if tests were applicable. The most restrictive criterium of exclusion was that a meta-analysis has to have at least ten studies. Thus, in the data that is scrutinized, there has been enforced and ongoing research. \citet{ioannidis.2005} state that publication bias is also a consequence of modern discovery oriented research, and thus it may well be that publication bias is also an issue when the number of studies are lower.\\

>>>>

meta.data <- data.ext2 %>% filter(meta.id %in% meta.f$meta.id)

@@

\section{Interpretation}
In this study, a proportion of the meta-analyses that have been scrutinized have publication bias. Since regression and rank test have been applied one-sided, they have very likely larger effects in smaller studies that in larger studies. \\
There have been proposed a number of reasons for this tendencies in smaller studies (see \citet{Egger} for a thorough discussion). In clinical settings, it might be that the requirement for more study participants in large studies might systematically change the study population. However, this systematic differences could influence the results in two ways: If recruitement of participants with a disease is difficult, and thus, also participants with less severe types of the disease are included, it might be that the effect of treatment is larger in the smaller study. But one could also argue that the opposite could eventually be the case. \\
The main cause for funnel plot asymmetry with smaller studies having larger effects is publication bias. Publication bias enforces questionable research practices from researchers such as selective outcome reporting, $p$-hacking and data fabrication. Larger studies are less affected, and have also in general higher methodological quality \citep{Egger}, which leads to smaller effect sizes.\\
Presence of publication bias in meta-analyses can ultimately lead to patient harm, because decision makers in clinical practice use the meta-analyses to take decisions if they use a treatment. On the swiss Cochrane website, it is stated that Cochrane is the ``single most reliable source of evidence on the effects of health care''. However, publication bias does in general lead to too large confidence in the results of the meta-analyses. In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias. Besides harm to patient, this can cause a waste of ressources. \\
The comparison of the results with previous analyses of publication bias in the Cochrane Database of Systematic Reviews implies gives more confidence in the results of this study, because they are largely in line. \\
The term publication bias is frequently used in this study, but \Sexpr{round((length(which(meta.data$study.data_source == "UNPUB"))/dim(meta.data)[1])*100, 1)}\% of the analysis dataset (1) are unpublished results. This mitigates the estimated extent of publication bias in this study since it has been shown repeatedly that effects in the grey literature are smaller.

@@

After application of the criteria of \citet{Ioannidis2007}, there are left \Sexpr{round((740/6354)*100, 1)} \% of the reviews and \Sexpr{round((23243/70662)*100, 1)}\% of the studies. It is not clear how the results would be in the remaining dataset if tests were applicable. The most restrictive criterium of exclusion was that a meta-analysis has to have at least ten studies. Thus, in the data that is scrutinized, there has been enforced and ongoing research. \citet{ioannidis.2005} state that publication bias is also a consequence of modern discovery oriented research, and thus it may well be that publication bias is also an issue when the number of studies are lower. Also, it is possible that by excluding meta-analyses where $I^2 \geq 0.5$, the most extreme cases of publication bias are removed since publication bias increases the between-study heterogeneity.\\
Furthermore, the sub-partitioning of meta-analyses based on conparison, outcome and subgroup is only one possibility%, which is in fact not recommended by the Cochrane Organisation. 
Cochrane usually performs multiple meta-analyses with the same results, for example by doing sensitivity analyses (not an issue in this study, since they are removed) and subgroup analyses and overall analyses. One can as well repeat the analysis without considering subbgroups. This will have the advantage of increasing the sample size, but it will also result in increased heterogeneity in meta-analyses, and if one subgroup with small studies yields large effects, the cause must not be publication bias. \\
